\Title

### 2021-02-09 manuscript/content.tex
Start adding gradient boosting schematics figure
Add observation points, sources and caption to figure

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
This work contains British Geological Survey materials © UKRI.

>>>>

\begin{figure*}
    \includegraphics[width=\linewidth]{figs/gradient-boosting-schematics.pdf}
    \caption{
        Sketch of the gradient-boosting process.
        (a)~Set of observation points that simulate a ground survey.
        (b)~Location of the sources obtained by putting one source below each
        observation point.
        (c)~Sets of equivalent sources obtained through gradient-boosting by
        selecting only the ones that fall inside each overlapping window.
        Blue and orange dots represent the horizontal location of the
        observation points and the original sources, respectively.
        The dashed line squares represent the boundaries of each overlapping
        window, while its corresponding sources are symbolized through red
        dots.
        Grey dots represent the other sources that aren't included in that
        particular set.
    }
    \label{fig:gradient-boosting-schematics}
\end{figure*}

@@

We are indebted to the developers and maintainers of the open-source software
without which this work would not have been possible.
S.R. Soler is supported by a scholarship from CONICET, Argentina.
This work contains British Geological Survey materials ©~UKRI.
